---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---
```{r}
setwd("D:/Coursera/RProgramming/Repicable/RepData_PeerAssessment1")
```

## Loading and preprocessing the data
```{r}

data<- read.csv("activity.csv",stringsAsFactors=FALSE)
str(data)
data$date<-as.Date(data$date)
```


## What is mean total number of steps taken per day?

1. Make a histogram of the total number of steps taken each day


```{r}
sumDate<-tapply(data$steps,data$date,sum) 
hist(sumDate,main = paste("Histogram of total number of stpes"))
```

2. Calculate and report the **mean** and **median** total number of steps taken per day 
```{r}
mean(sumDate, na.rm=TRUE)
median(sumDate, na.rm=TRUE)
```


## What is the average daily activity pattern?
1. Make a time series plot (i.e. `type = "l"`) of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r}
dat <- aggregate(steps ~ interval, data, mean)
plot(dat$interval,dat$steps,type="l",xlab="Time interval", ylab="Average number of steps")
````


2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r}
subset(dat,steps==max(steps),select=interval)
```
## Imputing missing values
1. Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with `NA`s)

```{r}
length(which(is.na(data$steps)))
```

Missing value will fill by median value of each time interval of the day
```{r}
temmedian<- aggregate(steps ~ interval, data, median)
tem<-merge(x=data,y=temmedian,by="interval",all.x=TRUE)
names(tem)

for (i in 1:nrow(tem)){
        if (is.na(tem$steps.x[i])){
                tem$steps[i]<-tem$steps.y[i]
        }else{
                tem$steps[i]<-tem$steps.x[i]
        }
        
}
nonNA<-tem[,c(1,3,5)]

```
A histogram of the total number of steps taken each day and Calculate and report the mean and median 
```{r}
totalSteps<-tapply(nonNA$steps,nonNA$date,sum) 
hist(totalSteps,main = paste("Histogram of total number of stpes from Non NA dataset"))
mean(totalSteps)
median(totalSteps)
```
The histogram from new dataset where NA were replace with the median value of the same time interval each day, only one different we see is the frequency of 0 increase. When compute mean and median value from the new dataset both of them are decrese to 9503.869 and 10395 respectively as because number of N is increase where the value of them is 0. 


## Are there differences in activity patterns between weekdays and weekends?
Create weekday variable
```{r}
nonNA$day<-weekdays(nonNA$date)
nonNA$weekday[nonNA$day %in% c("Monday","Tuesday", "Wednesday", "Thursday", "Friday")] <- "Weekdays"
nonNA$weekday[nonNA$day %in% c("Saturday","Sunday")] <- "Weekend" 
weekday = factor(nonNA$weekday,levels=c("Weekdays","Weekend"))
```

```{r}

library(ggplot2)

dataplot <- aggregate(steps ~ interval+weekday , nonNA, mean)
dataplot$weekday<-as.factor(dataplot$weekday)

p<-ggplot(dataplot, aes(x=interval, y=steps, group=weekday))
p + geom_line(aes(colour = weekday)) + facet_grid(weekday ~ .) 
```