---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---
```{r}
setwd("D:/Coursera/RProgramming/Repicable/RepData_PeerAssessment1")
```

## Loading and preprocessing the data
```{r}

data<- read.csv("activity.csv",stringsAsFactors=FALSE)
str(data)
data$date<-as.Date(data$date)
```


## What is mean total number of steps taken per day?

1. Make a histogram of the total number of steps taken each day


```{r}
sumDate<-tapply(data$steps,data$date,sum) 
hist(sumDate,main = paste("Histogram of total number of stpes"))
```

2. Calculate and report the **mean** and **median** total number of steps taken per day 
```{r}
mean(sumDate, na.rm=TRUE)
median(sumDate, na.rm=TRUE)
```


## What is the average daily activity pattern?
1. Make a time series plot (i.e. `type = "l"`) of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r}
dat <- aggregate(steps ~ interval, data, mean)
plot(dat$interval,dat$steps,type="l",xlab="Time interval", ylab="Average number of steps")
````


2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r}
subset(dat,steps==max(steps),select=interval)
```
## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
